Conjure: Summoning Proxies from Unused Address Space

### 2019-09-26 paper/background.tex
refraction networking -> Refraction Networking

Refraction networking operates by injecting covert communication inside a
client's HTTPS connection with a reachable site, also known as a decoy site. In
a regular HTTPS session, a client establishes a TCP connection, performs a TLS
handshake with a destination site, sends an encrypted web request, and
receives an encrypted response. In Refraction Networking, at least one direction
of this exchange is observed by a \emph{refraction station}, deployed at
some Internet service provider (ISP). The station watches for a covert signal from
the client that this connection is to be used for censorship circumvention.
Upon seeing the signal, the station will take over the HTTPS session,
and establish a proxy session with the client that can then be used for covert
communication.

@@

One of the key challenges for refraction networking is in taking over a session. The station must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client. A simple approach is to have the refraction station act as an inline transparent proxy (Figure~\ref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site. After a TLS handshake has been completed, the station terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.

@@

\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the station to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}. In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibility for the amount of data that can be sent with the registration.

>>>>

Refraction Networking operates by injecting covert communication inside a
client's HTTPS connection with a reachable site, also known as a decoy site. In
a regular HTTPS session, a client establishes a TCP connection, performs a TLS
handshake with a destination site, sends an encrypted web request, and
receives an encrypted response. In Refraction Networking, at least one direction
of this exchange is observed by a \emph{refraction station}, deployed at
some Internet service provider (ISP). The station watches for a covert signal from
the client that this connection is to be used for censorship circumvention.
Upon seeing the signal, the station will take over the HTTPS session,
and establish a proxy session with the client that can then be used for covert
communication.

@@

One of the key challenges for Refraction Networking is in taking over a session. The station must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client. A simple approach is to have the refraction station act as an inline transparent proxy (Figure~\ref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site. After a TLS handshake has been completed, the station terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.

@@

\paragraph{Registration Signal} In all implementations of Refraction Networking, a client must send a covert signal to the station to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}. In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibility for the amount of data that can be sent with the registration.
